Kyoto VR MQP Paper First Draft

### 2019-09-23 paper.tex
another testing section and more figures

\subsection{Testing ARuko}
\label{sec:testingARuko}

>>>>

\subsection{Testing Taking a Tour with ARuko}
\label{sec:testingARuko}

Because it was not feasible to travel to Kinkaku-ji every time we needed to
test the GPS functionality of the app, we used Editour to design an example
tour around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed
us to catch various bugs before we created a finalized prototype for
field-testing at Kinkaku-ji. The tour represented in \ref{fig:ritsuTour} is
what we used for testing the app. The ``C-Shaped Region'' helped us test
concave regions. This unique region also prompted us to think about what UI
behavior made the most sense if a user were to walk into a region, walk out and
then in again. We decided that it was awkward if the audio restarted upon
re-entering a region, since the audio would still be playing once a user left
the region. The region at the bottom surrounding our domitories was added for
our convenience, allowing us to test the app while we were away from the lab.
As we began to implement more complex UI that changed based on GPS position in
various ways, directly taking the tour by walking around was an invaluable way
to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
in the late stages of the project. Having a way to regularly run field tests
was integral to polishing the app in time before we revisited Kinkaku-ji.
Because the Editour was flexible enough to easily swap out media and add
regions to the tour, the Editour proved itself to be as helpful for testing as
it was for crafting the final tour that could be taken at Kinkaku-ji.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{ritsu-tour.png}
	\caption{The Ritsumeikan example tour used for testing}
	\label{fig:ritsuTour}
\end{figure}
